%-------------------------
% ATS-Optimized Resume – Piyush Kumar (Single Page)
% Compiler: pdflatex / xelatex
%-------------------------
\documentclass[letterpaper,10pt]{article}

\usepackage[left=0.5in, right=0.5in, top=0.35in, bottom=0.35in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}


\hypersetup{colorlinks=false, pdfborder={0 0 0}}

\titleformat{\section}{\bfseries\normalsize}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{5pt}{3pt}

\setlist[itemize]{leftmargin=1.4em, itemsep=0pt, topsep=1pt, parsep=0pt}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

\newcommand{\resumeItem}[1]{\item\small #1}

\newcommand{\expEntry}[4]{%
  \noindent{\textbf{#1} \hfill \textbf{#3}}\\[-2pt]
  {\small\textit{#2} \hfill \textit{#4}}%
}

\newcommand{\projEntry}[2]{%
  \noindent{\textbf{#1} $|$ \textit{\small #2}}%
}

\begin{document}


%---------- HEADER ----------
\begin{center}
  {\Large \textbf{PIYUSH KUMAR}}\\[2pt]
  \small
  \href{mailto:piyushkumar63072@gmail.com}{piyushkumar63072@gmail.com} \;$\cdot$\;
  +91-7564843698 \;$\cdot$\;
  \href{https://linkedin.com/in/piyush-kumar-375265331}{linkedin.com/in/piyush-kumar-375265331} \;$\cdot$\;
  \href{https://github.com/Piyush75812}{github.com/Piyush75812}
\end{center}


\vspace{2pt}

%---------- PROFESSIONAL SUMMARY ----------
\section{Professional Summary}
\small Results-driven MCA student and aspiring \textbf{MERN Stack / Full Stack Developer} with hands-on industry internship experience building responsive web applications using \textbf{React.js, Node.js, Express.js, MongoDB,} and \textbf{MySQL}. Proficient in REST API development, CRUD operations, and mobile-first UI/UX design. Seeking a \textbf{Software Engineer, MERN Stack Developer,} or \textbf{Web Developer} role to deliver scalable, user-centric solutions.

\vspace{2pt}

%---------- TECHNICAL SKILLS ----------
\section{Technical Skills}
\small
\begin{itemize}[leftmargin=0pt, label={}, itemsep=0pt, topsep=1pt]
  \item \textbf{Languages:} JavaScript (ES6+), Java, SQL, HTML5, CSS3
  \item \textbf{Frontend:} React.js, Bootstrap 5, Responsive Design, UI/UX Design
  \item \textbf{Backend:} Node.js, Express.js, REST APIs, CRUD Operations, MVC Architecture
  \item \textbf{Databases:} MongoDB, MySQL 
  
   \textbf{Tools:} Git, GitHub, VS Code, npm, Figma
\end{itemize}

\vspace{2pt}

%---------- INTERNSHIP EXPERIENCE ----------
\section{Internship Experience}
\expEntry{Web Development Intern}{Launched Global – Bengaluru (Remote)}{Apr 2025 – Jun 2025}{}
\begin{itemize}
  \resumeItem{Engineered \textbf{5+ responsive web applications} using HTML5, CSS3, JavaScript, and Bootstrap, improving cross-device compatibility by \textbf{40\%}.}
  \resumeItem{Worked on UI/UX improvements to enhance user experience, navigation, and website accessibility.}
  \resumeItem{Collaborated with the development team to create clean, interactive, and user-centric web designs.}
  \resumeItem{Improved website performance and usability by applying modern web design principles.

}
\end{itemize}

\vspace{2pt}

%---------- PROJECTS ----------
\section{Projects}

\projEntry{Student Management System}{HTML5, CSS3, Bootstrap, JavaScript, Node.js, Express.js, MySQL \hfill 2025}
\begin{itemize}
  \resumeItem{Built a full-stack \textbf{CRUD web application} managing \textbf{100+ student records} (enrollment, grades, attendance) with a secure Node.js/Express.js REST API backend.}
  \resumeItem{Designed a normalized \textbf{MySQL relational database schema} reducing data redundancy by \textbf{35\%} and ensuring referential integrity.}
  \resumeItem{Delivered a fully \textbf{responsive Bootstrap UI} ensuring consistent UX across desktop and mobile platforms.}
\end{itemize}

\vspace{3pt}
\projEntry{Time Table Scheduler}{HTML5, CSS3, Bootstrap, JavaScript, Node.js, Express.js, MongoDB \hfill 2025}
\begin{itemize}
  \resumeItem{Built an automated timetable scheduling application.}
  \resumeItem{Integrated \textbf{MongoDB} for flexible, schema-free storage of schedules, subjects, and faculty data with real-time CRUD via Express.js REST APIs.}
  \resumeItem{Designed user-friendly dashboard and forms for timetable management.}
\end{itemize}

\vspace{2pt}

%---------- EDUCATION ----------
\section{Education}
\expEntry{Master of Computer Applications (MCA)}{G. L. Bajaj Institute of Technology \& Management, Greater Noida}{2024 – 2026}{}

\vspace{3pt}
\expEntry{Bachelor of Computer Applications (BCA)}{M. P. Sinha Science College, Muzaffarpur}{2021 – 2024}{}

\vspace{2pt}

%---------- CERTIFICATIONS ----------
\section{Certifications}
\small
\begin{itemize}
  \resumeItem{\textbf{SQL (Basic)} – HackerRank \hfill 2025}
  \resumeItem{\textbf{Programming in Java} – NPTEL, IIT Madras \hfill 2025}
\end{itemize}

\vspace{2pt}

%---------- ACHIEVEMENTS ----------
\section{Achievements}
\small
\begin{itemize}
  \resumeItem{Completed a \textbf{professional industry internship} at Launched Global, Bengaluru, delivering production-ready responsive web applications.}
  \resumeItem{Independently developed \textbf{2 full-stack web applications} integrating React/Node.js frontend, Express.js backend, and relational/non-relational databases.}
  \resumeItem{Earned dual technical certifications: \textbf{HackerRank SQL} and \textbf{NPTEL Java (IIT Madras)}, demonstrating commitment to continuous upskilling.}
\end{itemize}

\end{document}
